### 2025-02-06 paper/sections/other/constraints.qmd
gotta revisit this

# Data:
# constraints = ["none", "both"]        # x1 cannot be mutated
constraints = ["both", "none"]        # x2 cannot be mutated
data = LinearlySeparable(
    n_train=500,
    batchsize=50,
    mutability=constraints
)
ce_data = get_ce_data(data)
val_size = data.n_validation / (data.n_validation + data.n_train)
train_set, val_set, _ = train_val_split(data, ce_data, val_size)

>>>>

# Data:
# constraints = ["none", "both"]        # x1 cannot be mutated
constraints = ["both", "both"]        # x2 cannot be mutated
data = LinearlySeparable(
    n_train=500,
    batchsize=50,
    mutability=constraints
)
ce_data = get_ce_data(data)
val_size = data.n_validation / (data.n_validation + data.n_train)
train_set, val_set, _ = train_val_split(data, ce_data, val_size)
